---
title: "WQP data issues"
author: "Mark Hagemann"
date: "May 3, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Herein I list some issues common in data retrieved from the WQP.

1. Data structure
    - Different number of columns FIX: wqp_checkClasses
    - Column classes FIX: wqp_checkClasses
2. Data contents
    - missing units FIX: wqp_checkUnits
    - inconsistently reported units, e.g. "mg/l", "mg/L", "ppm", "mg/l as N" FIX: wqp_checkUnits
    - Missing fraction FIX: wqp_checkFraction
    - missing detection limit FIX: wqp_checkBDL
    - missing/inconsistent collection method
    - missing/inconsistent analytical method
    - inconsitent reporting of bdls FIX: wqp_checkBDL


```{r}

with(aluminumData, 
     summary(as.factor(ResultDetectionConditionText[is.na(ResultMeasureValue)])))

with(aluminumData, 
     summary(as.factor(ResultDetectionConditionText[!is.na(ResultMeasureValue)])))
```

So ALL NA's belong to BDL-reported values.

```{r}
foo <- Reduce(`*`, lapply(wqpData[badrows,], is.na))
summary(foo)

```



```{r}
setdiff(names(boundWQ), names(aluminumData))

sample(na.omit(boundWQ$valueType), 10)
unique(boundWQ$resultweightbasis)
sample(unique(boundWQ$resultparticlesizebasis), 10)

foo <- wqpData[stillbad2, ]

glimpse(foo)
sum(!is.na(foo$ResultMeasureValue))
unique(foo$ResultDetectionConditionText)
```

Checking BDLs

```{r}
summary(as.factor(wqpData$ResultDetectionConditionText))
summary(as.factor(wqpData$DetectionQuantitationLimitTypeName))
summary(wqpData$DetectionQuantitationLimitMeasure.MeasureValue)

# Can I get detection limit from analytical method?

wqpData %>%
  filter(!is.na(DetectionQuantitationLimitMeasure.MeasureValue),
         !is.na(ResultAnalyticalMethod.MethodIdentifier)) %>% 
  # group_by(ResultAnalyticalMethod.MethodIdentifier, 
  #          ResultAnalyticalMethod.MethodIdentifierContext) %>% 
  transmute(analyticMethod = ResultAnalyticalMethod.MethodIdentifier, 
         analyticContext = ResultAnalyticalMethod.MethodIdentifierContext,
         detlim = DetectionQuantitationLimitMeasure.MeasureValue,
         detunits = DetectionQuantitationLimitMeasure.MeasureUnitCode) %>% 
  # ungroup() %>% 
  unique() %>% 
  arrange(analyticMethod, analyticContext) %>% 
  print(n = 40)
```

Bottom line: Can't infer detection limit from analytical method. 


```{r}
sample_n(wqpData[badrows, ], 10) %>% glimpse
sample_n(wqpData[goodrows, ], 10) %>% glimpse

wqpData %>% 
  filter(badrows) %>% 
  filter(ResultCommentText != "") %>% 
  glimpse
```

Does aluminumData have rows that are missing detlim info but that come from a dataset that does have such info?
```{r}
aluminumData %>% 
  group_by(CharacteristicName,
        ResultSampleFractionText,
        MonitoringLocationIdentifier) %>% 
  
```

