---
title: "notebook20160531"
author: "Mark Hagemann"
date: "May 31, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Improving retrieval vignette.

- simplifying data
- Combine wqpData to rcData


Tracking down a warning when simplifying no3Data to purge redundant units.

- I think it comes from the Mode function.
- text is `In c("mg/l", "mg/l as N", "mg/l", "mg/l as N", "mg/l",  ... :
  longer object length is not a multiple of shorter object length`

```{r}
debug(Mode)
no3Simple <- wqp_simplifyConc(no3Data, average = "time")
```

OK, fixed that. It was improperly specified formula for mutate_ (NSE stuff)

Now I'm testing out the creation of rcData objects via makeRcData(simpleConc, simpleFlow)

```{r}
rcDataList <- makeRcData(simpleConc = no3Simple, simpleFlow = qSimple)
rawDataList <- makeRcData(simpleConc = no3Simple, simpleFlow = qSimple, type = "raw")
length(rcDataList)
nobs <- sapply(rcDataList, nrow)
nbdl <- sapply(rcDataList, function(df) sum(df$is.bdl))

sum(nobs > 30 & nbdl == 0)
min(which(nobs >= 30))

rcDataList <- rcDataList[nobs >= 30 & nbdl == 0]
rawDataList <- rawDataList[nobs >= 30 & nbdl == 0]


foo <- loadest_cal(rcDataList[[1]])
rcDataList[[1]]
glimpse(rawDataList[[1]])
rawDataList[[1]] %>% 
  plot(conc ~ flow, .)


makeModelData(rawDataList[[1]])
```

Need to debug makeModelData. For some reason it's giving NaN for c.

```{r}
debug(makeModelData)
makeModelData(rawDataList[[1]])
```

Hmm. Problem is zeros in concentration data. Not very likely, especially with nitrate. Should treat these as bdl. 

- is there any detection limit info?

```{r}
rawDataList[[1]]

no3Data %>% 
  filter(MonitoringLocationIdentifier == "MDEDAT04_WQX-SID0112",
         CharacteristicName == "Nitrate",
         ResultSampleFractionText == "Dissolved") %>% 
  glimpse()
```

None. Could put artificial detection limit at minimum nonzero observation. In any case, zeros should be treated as BDL. 

OK, fixed that--need to just omit datasets with zeros for now. But now I'm getting NaN flow values (in the *raw* data)

```{r}

glimpse(rawDataList[[1]])

qData %>% 
  filter(MonitoringLocationIdentifier == "USGS-01573750",
         ActivityStartDate == "2002-09-19") %>% 
  glimpse()
```

Fixed that too. 

STILL getting not enough data complaint.

```{r}
rawDataList[[3]] %>% 
  select(conc, flow) %>% 
  print(n = 50)
```

Which is USGS-01591510?

```{r}
at1 <- attr(no3Data, "siteInfo")

at1 %>% 
  filter(MonitoringLocationIdentifier == "USGS-01591510")
```

I should get rid of zero flow like I did NA flows. For the same reason, really (since NAs are BDLs) 
