---
title:"notebook20160526"
author:"MarkHagemann"
date:"May26,2016"
output:html_document
---

HAHA! I accidentally did a find and replace for " ", replacing with ""! good thing this was a pretty small notebook! I'm only going to fix what I need now. 

```{rsetup,include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

workingontimezoneconversion.

IhavetheOlsonnamesforeachrowinawqpdataset.FromthisIcan:

-createadatetimeobjectusingtheOlsonname
-formatitasUTCtime
-reconverttoPOSIXct

```{r}
times<-startdt
olsons<-wqpTZ

head(times)
head(olsons)

toUTC_oneTZ<-function(timestring,olsonstring,...){
psx1<-as.POSIXct(timestring,tz=olsonstring,...)
psx2<-as.POSIXct(format(psx1,tz="UTC",usetz=TRUE),tz="UTC")
}

toUTC<-function(timestring,olsonstring){
olsonstring<-as.factor(olsonstring)
timelist<-split(timestring,f=olsonstring)

utcList<-Map(toUTC_oneTZ,timestring=timelist,olsonstring=levels(olsonstring))
}

utctimes<-toUTC(times,olsons)

head(utctimes)
```

That'spretty.I'mproudofthat.

SoImovedthattothepackage,withsomeimprovementsandaddedtests.Nowwqp_checkTZappearstowork.


NextI'mmakingafunctiontoaverageoverdepth.FirstIwanttoseeifIneedtoperformchecks,e.g.usingthecommenttext.

```{r}
summary(as.factor(no3Data$ResultDepthAltitudeReferencePointText))
summary(as.factor(no3Data$ActivityDepthAltitudeReferencePointText))

no3Data%>%
group_by(ActivityDepthAltitudeReferencePointText)%>%
summarize(nas=sum(is.na(ActivityDepthHeightMeasure.MeasureValue)),
n=n())

no3Data%>%
filter(is.na(ActivityDepthAltitudeReferencePointText))%>%
select(ActivityDepthHeightMeasure.MeasureValue)%>%
summary()

no3Data%>%
filter(ActivityDepthAltitudeReferencePointText=="Belowland-surfacedatum")%>%
glimpse()

```

LookslikeIneedtomakea`wqp_checkDepth`function.ThisiswhereIshouldputtheunitconversionfordepth--notcheckUnits.

DONE.

NowestablishwhetherResultDepth...everprovidesadditionalinformationtoActivityDepth...

```{r}
nitrateData%>%
filter(is.na(ActivityDepthHeightMeasure.MeasureValue),
!is.na(ResultDepthHeightMeasure.MeasureValue))%>%
glimpse

```

Nope!



Ugh,somethingnotworkingrightinmysummaryofsimplifiedconcentrationdata.

```{r}
simp %>%
  group_by_(.dots = c("Date", "station", "char", "frac", "conc.units", "conc.flag", "detlim", "is.bdl")) %>% 
  summarize(conc = mean(conc))

simp %>%
  group_by_(~Date, ~station)
```

