---
title: "notebook20160525"
author: "Mark Hagemann"
date: "May 25, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

WQP should be done updating. Redo retrievals and resave objects.

- nope, looks like it's running late.

Meanwhile, average observations over depth

```{r}
no3Data %>% 
  filter(!is.na(ResultDepthHeightMeasure.MeasureValue),
         ResultDepthHeightMeasure.MeasureValue != 0) %>% 
  glimpse

```

So nothing that isn't at zero depth.

```{r}
qData %>% 
  filter(!is.na(ResultDepthHeightMeasure.MeasureValue),
         ResultDepthHeightMeasure.MeasureValue != 0) %>% 
  glimpse
```

But should be looking at ActivityDepth

```{r}
hasdepth <- no3Data %>% 
  filter(!is.na(ActivityDepthHeightMeasure.MeasureValue),
         ActivityDepthHeightMeasure.MeasureValue != 0)

glimpse(hasdepth)

```

How is this defined? I don't believe they're making observations in a river at 18m depth.


```{r}
hasdepth %>% 
  group_by(MonitoringLocationIdentifier) %>% 
  summarize(mindepth = min(ActivityDepthHeightMeasure.MeasureValue),
            maxdepth = max(ActivityDepthHeightMeasure.MeasureValue),
            meandepth = mean(ActivityDepthHeightMeasure.MeasureValue),
            n = n()) %>% 
  arrange(desc(maxdepth))

summary(as.factor(hasdepth$ActivityDepthHeightMeasure.MeasureUnitCode))

```

So I'll need to convert the depth in checkUnits as well. 


```{r}
summary(as.factor(hasdepth$ActivityDepthAltitudeReferencePointText))
```

That's DONE.

### Function to check timezones

```{r}
summary(as.factor(no3Data$ActivityStartTime.TimeZoneCode))

no3Data %>% 
  group_by(ActivityStartTime.TimeZoneCode) %>% 
  summarize(numna = sum(is.na(ActivityStartTime.Time)),
            numReported = n() - numna)

```

So a large chunk is reported but has no timezone.

```{r}
no3Data %>% 
  filter(is.na(ActivityStartTime.TimeZoneCode),
         !is.na(ActivityStartTime.Time)) %>% 
  mutate(starttime = as.factor(ActivityStartTime.Time)) %>% 
  summary()

qData %>% 
  filter(is.na(ActivityStartTime.TimeZoneCode),
         !is.na(ActivityStartTime.Time)) %>% 
  mutate(starttime = as.factor(ActivityStartTime.Time)) %>% 
  summary()
  
```

All the data missing timezones are reported as 00:00:00. 

- Since this is misleading, remove this information
- How to treat datetime column? options:
    1. remove these rows (make NA)
    2. report start and end time as separate columns
    3. encode the information that time is unknown.

I like option 2 the best. Use ActivityEndDateTime.


